A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-18 doc/large_strain.tex
finally get to the correct weak form

%
% Deformation gradient
%
Linear deformation map is assumed
$\d \gz x = \gz F \cdot \d \gz X$,
where $\gz F := \Grad \, \gz \varphi \equiv \gz I + \Grad \, \gz u$ is called deformation gradient.
The mapping has to be one-to-one and exclude a self penetration, consequently the Jacobian has to be positive $J = \det \gz F > 0$.
Deformation gradient can be split in the proper orthogonal rotation tensor $\gz R$ and the symmetric right $\gz U$ and left $\gz V$ stretch tensors as $\gz F = \gz R \gz U = \gz V \gz R$.
%
% strain measures
%
In what follows we characterize the material behavior using the Green-Lagrange strain tensor $\gz E:=\frac{1}{2}\left[\gz C - \gz I\right]$, where $\gz C$ is right Cauchy-Green tensor $\gz C := \gz F^T \cdot \gz F = \gz U^2$. Clearly $J = \sqrt{\det \gz C}$ and $\partial (\bullet)/\partial \gz E = 2\, \partial (\bullet)/\partial \gz C$.

For conservative systems without the volumetric load the total potential energy functional $\mcl E$ is introduced as
\begin{align}
\mcl E =
\int_{\mcl B_0} \mcl \psi(\gz C) \d V \,
- \int_{\partial \mcl B_0^N} \gz T \cdot \gz u \d S \, ,
\end{align}
where $\gz T$ is the prescribed loading at the Neumann part of the boundary $\partial \mcl B_0^N$ in reference configuration, $\mcl \psi$ denotes the strain-energy per unit reference volume and $\gz u$ should satisfy the prescribed Dirichlet boundary conditions $\gz u = \gz u^D$ on $\partial \mcl B_0^D := \partial \mcl B_0 \setminus \partial \mcl B_0^N \neq \emptyset $.

The principal of stationary potential energy requires that at the equilibriums the directional derivative with respect to the displacement $\gz u$
\begin{align}
\delta \mcl E =
\frac{\d}{\d \epsilon} \mcl E (\gz u + \epsilon \delta \gz u) \Bigr\rvert_{\epsilon=0}  = 0 \, .
\label{eq:stationary}
\end{align}
vanishes for all directions $\delta \gz u$ which satisfy homogeneous Dirichlet boundary conditions.
%
This leads to the following non-linear equation
\begin{align}
F(\gz u, \delta \gz u) =
\int_{\mcl B_0} \gz S : \delta \gz E \d V \,
-
\int_{\partial \mcl B_0^N} \gz T \cdot \delta \gz u \d S
= 0 \, ,
\end{align}
where $\gz S := 2\, \partial \mcl \psi / \partial \gz C$ is the second Piola-Kirchhoff stress tensor.

>>>>

%
% Deformation gradient
%
Linear deformation map is assumed
$\d \gz x = \gz F \cdot \d \gz X$,
where $\gz F := \Grad \, \gz \varphi \equiv \gz I + \Grad \, \gz u$ is called deformation gradient.
The mapping has to be one-to-one and exclude a self penetration, consequently the Jacobian has to be positive $J = \det \gz F > 0$.
Deformation gradient can be split in the proper orthogonal rotation tensor $\gz R$ and the symmetric right $\gz U$ and left $\gz V$ stretch tensors as $\gz F = \gz R \gz U = \gz V \gz R$.
%
% strain measures
%
In what follows we characterize the material behavior using the Green-Lagrange strain tensor $\gz E:=\frac{1}{2}\left[\gz C - \gz I\right]$, where $\gz C$ is right Cauchy-Green tensor $\gz C := \gz F^T \cdot \gz F = \gz U^2$. Clearly $J = \sqrt{\det \gz C}$ and $\partial (\bullet)/\partial \gz E = 2\, \partial (\bullet)/\partial \gz C$. We will also use the left Cauchy-Green tensor $\gz b := \gz F \cdot \gz F^T = \gz V^2$.

For conservative systems without the volumetric load the total potential energy functional $\mcl E$ is introduced as
\begin{align}
\mcl E =
\int_{\mcl B_0} \mcl \psi(\gz F) \d V \,
- \int_{\partial \mcl B_0^N} \overline{\gz T} \cdot \gz u \d S \, ,
\end{align}
where $\overline{\gz T}$ is the prescribed loading at the Neumann part of the boundary $\partial \mcl B_0^N$ in reference configuration, $\mcl \psi$ denotes the strain-energy per unit reference volume and $\gz u$ should satisfy the prescribed Dirichlet boundary conditions $\gz u = \overline{\gz u}$ on $\partial \mcl B_0^D := \partial \mcl B_0 \setminus \partial \mcl B_0^N \neq \emptyset $.

The principal of stationary potential energy requires that at the equilibriums the directional derivative with respect to the displacement $\gz u$
\begin{align}
\delta \mcl E =
\frac{\d}{\d \epsilon} \mcl E (\gz u + \epsilon \delta \gz u) \Bigr\rvert_{\epsilon=0}  = 0 \, .
\label{eq:stationary}
\end{align}
vanishes for all directions $\delta \gz u$ which satisfy homogeneous Dirichlet boundary conditions.
%
This leads to the following scalar non-linear equation
\begin{align}
F(\gz u, \delta \gz u) =
\int_{\mcl B_0} \gz P : \Grad \, \delta \gz u \d V \,
-
\int_{\partial \mcl B_0^N} \overline{\gz T} \cdot \delta \gz u \d S
= 0 \, ,
\end{align}
where $\gz P := \partial \mcl \psi / \partial \gz F$ is the first Piola-Kirchhoff stress tensor.
The double contraction in the first term can be re-written in terms of the symmetric Kirchhoff stress tensor $\gz \tau := \gz P \cdot \gz F^T$ as
\begin{align}
\gz P : \Grad \, \delta \gz u =
(\gz \tau \cdot \gz F^{-T}) : \Grad \, \delta \gz u =
\gz \tau : (\Grad \, \delta \gz u : \gz F^{-1}) =
\gz \tau : \grad \, \delta \gz u \, ,
\end{align}
and therefore
\begin{align}
  F(\gz u, \delta \gz u) =
  \int_{\mcl B_0} \gz \tau : \grad \, \delta \gz u \d V \,
  -
  \int_{\partial \mcl B_0^N} \overline{\gz T} \cdot \delta \gz u \d S
  = 0 \, .
\end{align}
Note that $\gz \tau$ is the Piola transformation of the second Piola-Kirchhoff stress $\gz S := \partial \mcl \psi / \partial \gz E \equiv 2 \partial \mcl \psi / \partial \gz C$,
that is $\gz \tau = \gz F \cdot \gz S \cdot \gz F^T$.
